Combined annotation exploration for SCPCP000006

### 2025-01-27 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r fig.width=10, fig.height=10, out.width='100%', results='asis'}
cell_type_df <- cell_type_df |>
  mutate(has_cnv_score = rowSums(cell_type_df[, grepl("has_cnv_chr", colnames(cell_type_df))])) |>
  mutate(has_cnv_score = case_when(
    has_cnv_score > params$cnv_threshold +2 ~ "CNV",
    has_cnv_score <= params$cnv_threshold ~ "no CNV",
    .default = "unknown"
  ))

>>>>

```{r fig.width=10, fig.height=10, out.width='100%', results='asis'}
cell_type_df <- cell_type_df |>
  mutate(has_cnv_score = rowSums(cell_type_df[, grepl("has_cnv_chr", colnames(cell_type_df))])) |>
  mutate(has_cnv_score = case_when(
    has_cnv_score > (params$cnv_threshold +2) ~ "CNV",
    has_cnv_score <= params$cnv_threshold ~ "no CNV",
    .default = "unknown"
  ))
